---
title: "Covariates subset and finite samples"
author:
  - Charlotte Voinot [Inria, Sanofi]
date: "Mai 2023"
output:
  html_document:
    code_folding: "hide"
    number_sections: no
    toc: yes
    toc_depth: 2
  pdf_document:
    toc: yes
abstract: | 
  Results & plots. 
---

```{r setup}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)

# Reproducibility
set.seed(123)

# Libraries
library(dplyr) # case_when and others
library(ggplot2)

```

In this simulations set-up, non-linear and complex surface responses and propensity scores are generated from the covariates.  The simulations set is taken from Nie and Wager (2020), where the three generative process simulated are highly non-linear.

Data set A : 
```{r}
#non linear estimator (forest) on non linear Wager dataset 
non.linear_A <- read.csv("C:/Users/I0566478/OneDrive - Sanofi/Charlotte/Bibliographie/Benedicte Projet/finite_sample/data/A.csv")
non.linear_A$sample.size <- as.factor(non.linear_A$sample.size )

#linear estimator on non linear Wager dataset  
linear_A <- read.csv("C:/Users/I0566478/OneDrive - Sanofi/Charlotte/Bibliographie/Benedicte Projet/finite_sample/data/A_linear.csv")
linear_A$sample.size <- as.factor(linear_A$sample.size )

#fusion of the two 
dataset_A <- rbind(non.linear_A,linear_A)
```


```{r}
ggplot(dataset_A, aes(x = sample.size, y = estimate, fill = subset)) +
  geom_boxplot(alpha = 0.8) +
  theme_minimal() +
  facet_grid(~nuisance, scales = 'free') +
  theme(strip.background = element_rect(colour="black", fill="white", 
                                       size=1.5, linetype="solid"))+
  geom_hline(yintercept = 0.9, linetype = "dashed", color = "darkblue")+
  geom_hline(yintercept = 0.50, linetype = "dashed", color = "red")
```
Keeping simple linear and logistic model of the covariates leads to a mispecification bias.

Data set B : 

```{r}
#non linear estimator (forest) on non linear Wager dataset 
non.linear_B <- read.csv("C:/Users/I0566478/OneDrive - Sanofi/Charlotte/Bibliographie/Benedicte Projet/finite_sample/data/B.csv")
non.linear_B$sample.size <- as.factor(non.linear_B$sample.size )

#linear estimator on non linear Wager dataset  
linear_B <- read.csv("C:/Users/I0566478/OneDrive - Sanofi/Charlotte/Bibliographie/Benedicte Projet/finite_sample/data/B_linear.csv")
linear_B$sample.size <- as.factor(linear_B$sample.size )

#fusion of the two 
dataset_B <- rbind(non.linear_B,linear_B)
```

```{r}
ggplot(dataset_B, aes(x = sample.size, y = estimate, fill = subset)) +
  geom_boxplot(alpha = 0.8) +
  theme_minimal() +
  facet_grid(~nuisance, scales = 'free') +
  theme(strip.background = element_rect(colour="black", fill="white", 
                                       size=1.5, linetype="solid"))+
  geom_hline(yintercept = 1, linetype = "dashed", color = "darkblue")+
  geom_hline(yintercept = 0.8, linetype = "dashed", color = "red")
```

Data set C 

```{r}
#non linear estimator (forest) on non linear Wager dataset 
non.linear_C <- read.csv("C:/Users/I0566478/OneDrive - Sanofi/Charlotte/Bibliographie/Benedicte Projet/finite_sample/data/C.csv")
non.linear_C$sample.size <- as.factor(non.linear_C$sample.size )

#linear estimator on non linear Wager dataset  
linear_C <- read.csv("C:/Users/I0566478/OneDrive - Sanofi/Charlotte/Bibliographie/Benedicte Projet/finite_sample/data/C_linear.csv")
linear_C$sample.size <- as.factor(linear_C$sample.size )

#fusion of the two 
dataset_C <- rbind(non.linear_C,linear_C)
```

```{r}
ggplot(dataset_C, aes(x = sample.size, y = estimate, fill = subset)) +
  geom_boxplot(alpha = 0.8) +
  theme_minimal() +
  facet_grid(~nuisance, scales = 'free') +
  theme(strip.background = element_rect(colour="black", fill="white", 
                                       size=1.5, linetype="solid"))+
  geom_hline(yintercept = 1, linetype = "dashed", color = "darkblue")+
  geom_hline(yintercept = 0.50, linetype = "dashed", color = "red")
```
Data set D 

```{r}
#non linear estimator (forest) on non linear Wager dataset 
non.linear_D <- read.csv("C:/Users/I0566478/OneDrive - Sanofi/Charlotte/Bibliographie/Benedicte Projet/finite_sample/data/D.csv")
non.linear_D$sample.size <- as.factor(non.linear_D$sample.size )

#linear estimator on non linear Wager dataset  
linear_D <- read.csv("C:/Users/I0566478/OneDrive - Sanofi/Charlotte/Bibliographie/Benedicte Projet/finite_sample/data/D_linear.csv")
linear_D$sample.size <- as.factor(linear_D$sample.size )

#fusion of the two 
dataset_D <- rbind(non.linear_D,linear_D)
```

```{r}
ggplot(dataset_D, aes(x = sample.size, y = estimate, fill = subset)) +
  geom_boxplot(alpha = 0.8) +
  theme_minimal() +
  facet_grid(~nuisance, scales = 'free') +
  theme(strip.background = element_rect(colour="black", fill="white", 
                                       size=1.5, linetype="solid"))+
  geom_hline(yintercept = 0.5, linetype = "dashed", color = "darkblue")+
  geom_hline(yintercept = 0.09, linetype = "dashed", color = "red")+
  ggtitle("")
```
